\documentclass{article}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=cyan,}
\usepackage{booktabs}
\usepackage{textgreek}

\input{../structure.tex} % Include the file specifying the document structure and custom commands

%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{Week 9 Pre-Lab}
\author{BIOE 320 Systems Physiology Laboratory} 
\date{}
%----------------------------------------------------------------------------------------

\begin{document}
\maketitle
\large

\begin{enumerate}
	\item What do you measure using an EOG?
	\item Define Saccades, Pursuit, and Vergence. Give an example of when you would observe each type of eye movement.
	\item Outline an experiment that you would like to perform in order to demonstrate one of Saccades, Pursuit, or Vergence. Make sure to include the eye movement you want to study, a description of the activity that you would evaluate (remember that you need a control and an experimental group) and the results you would expect to obtain from this experiment. When answering this question, take into consideration the feasibility of the experiment you are proposing.
	\begin{info}
	Your answer to this question and the amount of effort you put into planning your experiment will play a large role in your success during the lab. Answer this question as thoroughly and specifically as possible!	
	\end{info}

\end{enumerate}
\end{document}