\documentclass{article}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=cyan,}
\usepackage{booktabs}
\input{../structure.tex} % Include the file specifying the document structure and custom commands

%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{BIOE 320: Systems Physiology Laboratory}
\author{Spring 2023} 
\date{}
%----------------------------------------------------------------------------------------

\begin{document}

\maketitle
\subsection*{Instructor}
Dr. James Long\\
james.long@rice.edu\\
BRC 765

\subsection*{Teaching Assistants}
\begin{table}[h!]
	\centering
\begin{tabular}[h!]{ccc}
\textit{Monday} & \textit{Wednesday} & \textit{Thursday}\\
Zongru Li & Wonil Sohn & Matthew Lee\\
zongru.li@rice.edu & wws3@rice.edu & ml124@rice.edu
\end{tabular}
\end{table}

\subsection*{Office Hours}
Office hours are scheduled on a by-appointment basis. Please email the instructor to schedule a time.

\subsection*{Course Website}
The course website, which includes all necessary documents, is hosted on Github. You may access it through \href{https://jameslong12.github.io/BIOE320}{this link} or the following: \href{https://bit.ly/bioe320_s23}{bit.ly/bioe320\_s23}. Assignment submission and grading will be hosted on Canvas.

\subsection*{Course Description}
The primary objective of the laboratory course and selected assignments is to illustrate the physiological principles and processes that are described in BIOE 322, Systems Physiology. Using the BIOPAC software and various medical measurements tools, you will conduct physiological tests including ECG, EEG, EMG, blood pressure, pulmonary function, etc. with your partner(s).

Graded material includes: pre-lab assignments, in-class worksheets, and post-lab assignments.  There will be no quizzes or tests in this class. The pre-lab questions and post-lab questions are available on the course website. It is your responsibility to download and complete these assignments \textit{individually}. In-class assignments will be provided (one hard copy per group) at the beginning of the laboratory time.

\subsection*{Course Objectives}
By the end of the course, students will demonstrate the ability to:
\begin{enumerate}
	\item Conduct experiments with appropriate bioengineering techniques.
	\item Analyze and interpret data from living systems, using principles of human physiology.
	\item Design and execute a complete experiment.
\end{enumerate}

\subsection*{Corequisite}
Students must be concurrently enrolled in BIOE 322. No exceptions.

\subsection*{Safety}
Laboratory environments include inherent dangers and thus strict compliance to safety measures is important. All students are expected to work safely and to ask for assistance when uncertain. Absolutely no eating, drinking or gum chewing will be allowed at any place or time in the lab. Penalties of varying severity may be applied for lab safety violations, including but not limited to: improper use of equipment, leaving the lab area messy, endangering self or other students, and eating/drinking during lab.

\subsection*{Grading Policy}

This grading breakdown of the course is as follows:
\begin{table}[h!]
	\centering
\begin{tabular}[h!]{cccc}
\toprule
	Category & Submissions & Total Points & \% Final Grade\\
	\midrule
	Pre-Labs & Canvas & 125 & 25\%\\
	In-Labs & In class & 230 & 46\%\\
	Post-Labs & Canvas & 120 & 24\%\\
	Lab Conduct & In class & 25 & 5\%\\
	\bottomrule
\end{tabular}
\end{table}

There is no curve in this course -- what you see is you get! The earned letter grades will follow conventional numerical standards based on the cumulative percentage of assignment scores:
\begin{itemize}
	\item A+: $\geq 97$, A: $\geq 93$, A--: $\geq 90$
	\item B+: $\geq 87$, B: $\geq 83$, B--: $\geq 80$
	\item C+: $\geq 77$, C: $\geq 73$, C--: $\geq 70$
	\item D+: $\geq 67$, D: $\geq 63$, D--: $\geq 60$, F: $< 60$
\end{itemize}

\underline{Late assignments} will be penalized 30\% of the assignment value per day it is late, rounded up. In other words, if you submit a pre-lab one minute late on Canvas, you will automatically receive 30\% off the final grade. This penalty is intentionally steep - please turn in your assignments on time. If you believe that an error was made in grading your assignment, you should write a \underline{short} justification of your claim and email it to the instructor. The “statute of limitations” for submitting such claims is one week after the assignment was returned. Note that the entire assignment will be re-graded, not just the section in question, in order to ensure consistency and fairness.\\

Students are required to attend all sessions of the laboratory. Exceptions for illness, family emergencies, or other excusable absences may be granted with instructor approval on a case-by-case basis. Any make-ups for valid absences must be done at the convenience of the instructor and your lab partner. Penalties will also be assessed for tardiness; the point deduction will scale with the severity of the infraction.

\subsection*{Honor Code Policy}
Collaboration between group members is expected for the completion of high quality in-lab assignments. In contrast, you may not collaborate with other students, including those in your group, on pre-labs and post-labs. For these assignments, you are expected to turn in original work. Furthermore, for all assignments in this class, you may not consult the materials from previous years' BIOE 320 courses, including but not limited to: student assignments, reports, data calculations, and code. You may use academic sources, such as research papers, where appropriate, but you must cite these sources properly. Failure to cite work that is not your own is plagiarism and will be reported.

If you need clarification on any of these policies, please contact the instructor \textit{prior to submission} to avoid an infraction. For a list of standard definitions as outlined by the Honor Council, please see \href{https://cpb-us-e1.wpmucdn.com/blogs.rice.edu/dist/c/490/files/2022/08/Honor-Council-Standard-Definitions-and-Policies.pdf}{this link}.

\subsection*{Commitment to Equitable Learning}
This class is committed to an equitable learning environment. Accommodations will be made for students with alternative needs, but it is critical that you alert the instructor in advance of any additional resources you need prior to assignment submission. For additional resources and more information, please visit the \href{https://drc.rice.edu/}{Disability Resource Center} and the \href{https://aop.rice.edu/}{Access and Opportunity portal.}
\pagebreak
\subsection*{Schedule and Assignment List}
For assignments submitted through Canvas, the time of the due date is \textbf{midnight of the day before your scheduled lab date} unless otherwise noted. Please see the \href{https://registrar.rice.edu/calendars/spring-semester-2023}{Rice University Academic Calendar} for other important administrative dates.\\

\begin{table}[h!]
	\centering
\begin{tabular}[h!]{ccccc}
\toprule
	Date & Topic & Assignment & Submission & Points\\
	\midrule
	N/A & Lab conduct & & Class & 25\\
	\midrule
	Week of 01/09 & Week 1: Intro to BIOPAC & In-lab & Class & 25\\
		& & Post-lab & Canvas & 15\\
	\midrule
	Week of 01/16 & Martin Luther King, Jr. Day & &\\
	\midrule
	Week of 01/23 & Week 2: Electromyography (EMG) I & Pre-lab & Canvas & 15\\
		& & In-lab & Class & 25\\
		& & Post-lab & Canvas & 15\\
	Week of 01/30 & Week 3: Electromyography (EMG) II & Pre-lab & Canvas & 15\\
	 	& & In-lab & Class & 25\\
	 	& & Post-lab & Canvas & 15\\
	\midrule
	Week of 02/06 & Midterm recess & &\\
	\midrule
	Week of 02/13 & Week 4: Electroencephalography (EEG) & Pre-lab & Canvas & 15\\
	 	& & In-lab & Class & 25\\
	 	& & Post-lab & Canvas & 15\\
	Week of 02/20 & Week 5: Electrocardiography (ECG) I & Pre-lab & Canvas & 15\\
		& & In-lab & Class & 25\\
		& & Post-lab & Canvas & 15\\
	\midrule
	02/24 & Drop deadline & &\\
	\midrule
	Week of 02/27 & Week 6: Electrocardiography (ECG) II & Pre-lab & Canvas & 15\\
		& & In-lab & Class & 25\\
		& & Post-lab & Canvas & 15\\
	Week of 03/06 & Week 7: Blood Pressure (BP) & Pre-lab & Canvas & 15\\
		& & In-lab & Class & 25\\
		& & Post-lab & Canvas & 15\\
	\midrule
	Week of 03/13 & Spring recess & &\\
	\midrule
	Week of 03/20 & Week 8: Pulmonary Function (PF) & Pre-lab & Canvas & 15\\
		& & In-lab & Class & 25\\
		& & Post-lab & Canvas & 15\\
	\midrule
	Week of 03/27 & Beer Bike Week & & \\
	\midrule
	Week of 04/03 & Week 9: Electrooculography (EOG) & Pre-lab & Canvas & 20\\
		& & In-lab & Class & 30\\
	\bottomrule
	& & & Total points: & 500\\
\end{tabular}
\end{table}

\end{document}
